### 2018-05-03 papers/synth/example.tex
added

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[->,>=stealth',auto,node distance=5cm,
  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
  \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
  \node[main node] (ic) [below right of=ga,yshift=8mm,xshift=5mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
  \node[main node] (er) [below of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
  \node[main node,text width=2.5cm] (pm) [right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
  \node[main node] (ee) [right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
  \node[main node] (le) [below of=ee] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};

  \path (ic) edge[bend right] node [right] {\^{Qc6}} (ga);
  \path (er) edge[bend left] node [left] {R6} (ga);
  \path (er) edge[bend right] node [left] {\^{Qc6}} (ga);
  \path (er) edge[bend right] node [right] {\^{Qc6}} (ic);
  \path (ga) edge[bend right=80] node [right] {\^{Qc1}} (er);
  \path (ee) edge[bend left] node [left] {\^{R8},Qa7,Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
  \path (pm) edge[bend left=10] node [above] {{Qb2} Qc2} (ee);

  %ga->pm
  \path (ga) edge[bend left=10] node [above] {{Qb2} Qc2} (pm);
  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
  \end{tikzpicture}
  \caption{found-in-nature VTS}
  \label{fig:mukund-vts}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \begin{tikzpicture}[->,>=stealth',auto,node distance=5cm,
  thick,main node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
  \node[main node,text width=3cm] (ga) {GA{\small \^{Qa4} \^{Qa6} \^{Qb4} \^{Qb6} \^{Qc4} \^{R6}}};
  \node[main node] (ic) [below right of=ga,yshift=20mm,xshift=20mm] {IC {\small \^{Qa6} \^{Qb6} \^{R1}}};
  \node[main node] (er) [below right of=ga] {ER {\small \^{Qa1} \^{Qb1} \^{R1}}};
  \node[main node,text width=2.5cm] (pm) [above right of=ga] {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
  \node[main node] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
  \node[main node] (le) [above of=ee,yshift=-13mm,xshift=18mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};

  \path (ic) edge node [below] {\^{Qc6}} (ga);
  \path (er) edge[bend right=20] node [right] {\^{Qc6}} (ic);

  %er <> ga
  \path (er) edge[bend right=20] node [left] {\^{Qc6}} (ga);
  \path (er) edge[bend left=20] node [left] {R6} (ga);
  \path (ga) edge[bend right=40] node [left] {\^{Qc1}} (er);

  %ga <-> ee
  \path (ga) edge[bend left=25] node [above] {Qb2 Qc2} (ee);
  \path (ga) edge[bend left=10] node [above] {Qbc2/3} (ee);
  \path (ee) edge[bend left=0] node [below] {Qb2/3,Qa2,R2,\^{R4},Qc2/3} (ga);

  %le <-> pm
  \path (le) edge[bend right=10] node [above] {Qb7 Qc7} (pm);
  %ee -> le
  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7,Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=10] node [above] {\^{R3}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  %ga->pm
  \path (ga) edge[bend left=10] node [right] {{Qb2} Qc2} (pm);
  \path (ga) edge[bend left=80] node [above] {\^{R2}} (pm);
  \path (ga) edge[bend left=52] node [above] {\^{R7}} (pm);
  \path (ga) edge[bend left] node [above] {\^{R8}} (pm);
  \end{tikzpicture}
  \caption{found-in-nature VTS}
  \label{fig:mukund-vts}
\end{figure}
